Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-30 ms.tex
get of extraneous clear page.
this and that.

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
\hline
{Variable} & {Definition} \\
\hline
$M_{\bullet}$ & black hole mass \\
$\tilde{v}_{w}$ & total heating parameter, including minimum heating
rate from stellar and black hole velocity dispersion \\
$v_{w}$ & total heating parameter, excluding minimum heating rate from
velocity dispersion \\
$\sigma_0$ & stellar velocity dispersion (assumed to be radially constant)\\
$\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
$r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
$r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
$r_{\rm b}$ & outer break radius of stellar density profile \\ 
$r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
$\rho_{\star}(r)$ & 3D radial stellar density profile \\
$\rho(r)$ & gas density of CNM \\
$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
$M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
$q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
$\Gamma$ & power-law slope of radial stellar surface brightness
profile interior to the break radius \\
$\delta$ & power-law slope of the 3D stellar density profile inside of
the break radius, $\delta \equiv \Gamma+1$.\\
$\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
$\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
$t_{\rm h}$ & Hubble timescale \\
$\nu$ & gas density power-law slope at the stagnation radius
(eq.~[\ref{eq:densSlope}]) \\
\hline
\label{table:definitions}  
\end{tabular}
%\begin{tablenotes}
%\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

The accretion rate towards the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta M_{\star}|_{r_{\rm s}}}{\th} \nonumber \\
&\approx&
  \begin{cases}
    4.5 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    3.2 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where we have assumed $v_{w} \gg \sigma_0$ by adopting equation
(\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
given by
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    2.0 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
    1.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}
where $\dot{M}_{\rm edd} = 2.2M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
Eddington accretion rate, assuming a radiative efficiency of ten per
cent.  Note the sensitive dependence of the accretion rate on the wind
heating rate.  As will be discussed later,
equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on
relatively large scales and does not include outflows from the SMBH
accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}),
which may significantly reduce the fraction of $\dot{M}$ that actually
reaches the SMBH.

@@

\clearpage

@@

\citet{Sharma+2007} estimate the value of the radiative efficiency of
low luminosity AGN, $\epsilon_{\rm rad}$, based on MHD shearing box
simulations of collisionless plasmas.  For Eddington ratios of
relevance, their results (shown in their Fig.~6) are well approximated
by
\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  0.03 \left(\frac{\dot{M}_{\bullet}}{10^{-4}\dot{M}_{\rm edd}}\right)^{0.9} & \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim 10^{-4} \\
 0.03 &  10^{-2} \lsim \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim  10^{-4},
\end{cases}
\label{eq:efficiency}
\end{align}
where $\dot{M}_{\bullet}$ is the BH accretion (we use a more general
parametrization of the \citet{Sharma+2007} results in our numerical
results presented later).  In general $\dot{M}_{\bullet}$ will be
smaller than the inflow rate $\dot{M}$ calculated thus far by a factor
$\alpha < 1$ due to outflows from the accretion disk on small scales.
Thus, the full efficiency relating the mass inflow rate to the
radiative output is $\epsilon = \alpha \epsilon_{\rm rad}$, where we
take $\alpha = 0.1$ following \citet{Li+2013}, who find that the
fraction of the inflowing matter lost to outflows equals the
Shakura-Sunyaev viscosity parameter of the disk.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate
  $\dot{M}/\dot{M}_{\rm edd}$ as a function of black hole mass
  $M_{\bullet}$, shown for core ($\Gamma=0.1$, dot-dashed) and cusp
  galaxies ($\Gamma=0.8$, solid).  Black lines show the accretion rate
  calculated from equation (\ref{eq:eddr_analytic}) using the heating
  rate provided at $z = 0$ by the average star formation histories for
  each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the
  maximum accretion set by Ia supernovae blow-out, $\dot{M}_{\rm Ia}$
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate obtained if
  Compton heating acts alone, $\dot{M}_{\rm C}$
  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion
  rate for a thermally stable flow near the stagnation radius,
  $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the
  inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray
  circles), for NGC3115 from \citet{ShcherbakovWong+:2014a} (gray
  diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a}
  (gray triangles).  {\it Bottom panel:} Growth times $t_{\rm grow}
  \equiv \Mbh/\dot{M}_{\bullet}$ in units of the Hubble time $\th$ for
  each of the accretion rates shown in the top panel, where
  $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to
  account for the fraction of inflowing mass lost to disk outflows on
  small scales.}
\end{figure}

@@

Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
accretion rate as a function of black hole mass for the average star
formation heating, calculated from equation (\ref{eq:eddr_analytic})
using our results for the total wind heating
(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{8}M_{\sun}$.
These fall below the maximum thermally stable accretion rate,
$\dot{M}_{\rm TI}$ (yellow lines), although in practice high mass core
galaxies may be thermally unstable as we do not include the
$\zeta<\zeta_c$ criterion in Fig.~\ref{fig:mdot_mass} (see
equation~\eqref{eq:cooling4}).
% , although they become closer at the highest
% black hole masses $\sim 10^{9}M_{\odot}$.

For low mass black holes, blow out from SN Ia radius caps the SMBH
accretion rate at a value $\dot{M}_{\rm Ia} \sim
10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines;
eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
otherwise thermally-unstable flow at smaller radii.  For higher
$M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
heating contributes to the steady gas heating rate, even if the energy
released by a single Ia is insufficient to unbind gas from the stellar
bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and yellow lines mean at high $M_{\bullet}$.

@@

The unresolved core X-ray luminosities of nearby galactic nuclei
provide a powerful diagnostic of the SMBH accretion rates and how they
vary with SMBH mass and other galaxy properties (e.g., \citealt{Ho08}
and references therein).  Figure~\ref{fig:miller} shows our
predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a
function of black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm
  rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of
the inflowing matter loss to outflows from the accretion disk,
$\epsilon_{\rm rad}$ is the radiative efficiency of the accreted
matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric
correction into the measured X-ray band for low luminosity AGN
(\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
calculated using the average accretion rate for galaxies with core
($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) stellar density profiles,
using the mean power-law relationship $\Gamma = 0.3
\Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a}
galaxy sample.

@@

We have calculated steady-state models for the hot gaseous
circumnuclear media of quiescent galaxies, under the assumption that
gas is supplied exclusively by stellar wind mass loss and heated by
shocked stellar winds, supernovae and black hole feedback.  We compute
solutions for a range of different black hole masses, heating rates,
and observationally-motivated stellar density profiles.  Our numerical
results (Table \ref{table:models}) are used to verify and calibrate
analytic relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use
the latter to explore systematically how the SMBH accretion rate
varies with black hole mass and the galaxy's SFH.  Our results for
$\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray
luminosities of quiescent SMBHs and low luminosity AGN.  Our conclusions are summarized as follows.

@@

  \item Including the effects of heat transport by electron conduction
    results in at most order unity changes to the key properties of
    the flow (e.g. stagnation radius, mass accretion rate, and thermal
    stability) for causal values of the conduction saturation
    parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).  Angular
    momentum is also unlikely to invalidate our spherically symmetric
    model on large scales, given observationally inferred rotation rates of galactic nuclei
    near the stagnation radius ($\S\ref{sec:rotation}$). 
%However, on
 %   small scales gas would encounter a centrifugal barrier which would
  %  cause much of the gas flowing inwards on large scales to be driven
   % outwards in an outflow (as in \citealt{Li+2013}).

\item Radiative cooling has a more pronounced influence on the flow
  structure.  Cooling becomes important when the
  radiative cooling rate exceeds the gas heating rate near the
  stagnation radius, where the gas is in nearly hydrostatic equilibrium (Fig.~\ref{fig:TI}).  This condition is approximately equivalent to
  the $t_{\rm cool} \gg t_{\rm ff}$ criterion for thermal instability advocated by
  \citet{McCourt+12} and \citet{Li&Bryan14a}.  The transition in the flow properties that occurs as heating is reduced may represent a true ``thermal instability" (hot ISM condensing into a cooler clouds), or it may simply represent an abruption transition from a steady inflow-outflow solution to a global cooling flow.  We leave distinguishing between these possibilities to future work.

\item The location of the stagnation radius, and hence the SMBH
  accretion rate, is a sensitive function of the gas heating rate
  $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$, implying
  that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core (cusp) galaxies.
  However, $\Mdot$ can increase even more rapidly with decreasing
  $v_w$ for two reasons: (1) when $v_w$ becomes comparable to the
  stellar velocity dispersion ($\zeta < \zeta_c$;
  eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar
  bulge and cannot produce a flow with a positive kinetic energy
  interior to the stellar break radius, as we show in Appendix \ref{app:be}; (2)
  For low $v_w$, gas near the stagnation radius becomes thermally
  unstable, which based on the results of previous numerical studies
  (e.g.,\citealt{Ciotti+10}) is instead likely to result in
  time-dependent cycles of alternating high and low accretion phases
  ($\S\ref{sec:cycle}$).

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
  \hline
  {Variable} & {Definition} \\
  \hline
  $M_{\bullet}$ & black hole mass \\
  $\tilde{v}_{w}$ & total heating parameter, including minimum heating
  rate from stellar and black hole velocity dispersion \\
  $v_{w}$ & total heating parameter, excluding minimum heating rate from
  velocity dispersion \\
  $\sigma_{\bullet}$ & The line of sight velocity dispersion from the  $\Mbh-\sigma$ relation (eq.~\eqref{eq:Msigma})\\
  $\sigma_0$ & stellar velocity dispersion (assumed to be radially
  constant and equal to $\sqrt{3} \Mbh$).\\
  $\zeta$ & alternative heating parameter, $\zeta \equiv \sqrt{1 + (v_w/\sigma_0)^2}$ (eq.~[\ref{eq:zetacrit}])\\
  $r_{s}$ & stagnation radius, where gas radial velocity goes to zero \\
  $r_{\rm inf}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
  $r_{\rm b}$ & outer break radius of stellar density profile \\ 
  $r_{\rm Ia}$ & radius interior to which SN Ia are infrequent compared to the dynamical timescale (eq.~[\ref{eq:rIa}]) \\ 
  $\rho_{\star}(r)$ & 3D radial stellar density profile \\
  $\rho(r)$ & gas density of CNM \\
  $M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
  $M_{\rm enc}(r)$ & total enclosed mass inside radius $r$ (SMBH + stars) \\
  $q(r)$ & mass source term due to stellar winds, $q \propto \rho_{\star}$ (eq.~[\ref{eq:q}]) \\
  $\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
  $\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
  $\Gamma$ & power-law slope of radial stellar surface brightness
  profile interior to the break radius \\
  $\delta$ & power-law slope of the 3D stellar density profile inside of
  the break radius, $\delta \equiv \Gamma+1$.\\
  $\dot{M}$ & accretion rate (not necessarily equal to the SMBH accretion rate)   \\
  $\dot{M}_{\bullet}$ & SMBH accretion rate, $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha < 1$ accounts for outflows from the accretion disk on small scales.   \\
  $\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia (eq.~[\ref{eq:eddr_Ia}]) \\
  $\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating acting alone (eq.~[\ref{eq:MdotC}]) \\
  $\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
  $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
  $t_{\rm h}$ & Hubble timescale \\
  $\nu$ & gas density power-law slope at the stagnation radius
  (eq.~[\ref{eq:densSlope}]) \\
  \hline
\label{table:definitions}  
\end{tabular}
%\begin{tablenotes}
%\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

The accretion rate towards the SMBH is given by the total mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& 4\pi \int_{0}^{r_{s}}q r^{2}dr = \frac{\eta
    M_{\star}|_{r_{\rm s}}}{\th} = \frac{\eta \Mbh (\rs/\rinf)^{2-\Gamma}}{\th} \nonumber \\
  &\approx&
  \begin{cases}
    4.5 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    3.2 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}            
\end{eqnarray}
where we have assumed $v_{w} \gg \sigma_0$ by adopting equation
(\ref{eq:stag_simple}) for $r_s$.  The resulting Eddington ratio is
given by
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    2.0 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core}, \\
    1.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}
where $\dot{M}_{\rm edd} = 2.2M_{\bullet,8}M_{\odot}$ yr$^{-1}$ is the
Eddington accretion rate, assuming a radiative efficiency of ten per
cent.  Note the sensitive dependence of the accretion rate on the wind
heating rate.  As will be discussed later,
equation~\eqref{eq:eddr_analytic} is the radial mass inflow rate on
relatively large scales and does not include outflows from the SMBH
accretion disk (e.g.~\citealt{Blandford&Begelman99}; \citealt{Li+13}),
which may significantly reduce the fraction of $\dot{M}$ that actually
reaches the SMBH.

@@

%\clearpage

@@

\citet{Sharma+2007} estimate the value of the radiative efficiency of
low luminosity AGN, $\epsilon_{\rm rad}$, based on MHD shearing box
simulations of collisionless plasmas.  For Eddington ratios of
relevance, their results (shown in their Fig.~6) are well approximated
by
\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  0.03 \left(\frac{\dot{M}_{\bullet}}{10^{-4}\dot{M}_{\rm edd}}\right)^{0.9} & \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim 10^{-4} \\
 0.03 &  10^{-2} \lsim \frac{\dot{M}_{\bullet}}{\dot{M}_{\rm edd}} \lsim  10^{-4},
\end{cases}
\label{eq:efficiency}
\end{align}
where $\dot{M}_{\bullet}$ is the BH accretion rate. In general
$\dot{M}_{\bullet}$ will be smaller than the inflow rate $\dot{M}$
calculated thus far by a factor $\alpha < 1$ due to outflows from the
accretion disk on small scales.  Thus, the full efficiency relating
the mass inflow rate to the radiative output is $\epsilon = \alpha
\epsilon_{\rm rad}$, where we take $\alpha = 0.1$ following
\citet{Li+2013}, who find that the fraction of the inflowing matter
lost to outflows equals the Shakura-Sunyaev viscosity parameter of the
disk.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Gas inflow rate
  $\dot{M}/\dot{M}_{\rm edd}$ as a function of black hole mass
  $M_{\bullet}$, shown for core ($\Gamma=0.1$, dot-dashed) and cusp
  galaxies ($\Gamma=0.8$, solid).  Black lines show the accretion rate
  calculated from equation (\ref{eq:eddr_analytic}) using the heating
  rate provided at $z = 0$ by the average star formation histories for
  each galaxy mass (Fig.~\ref{fig:vwSources}).  Teal lines show the
  maximum accretion set by Ia supernovae blow-out or heating,
  $\dot{M}_{\rm Ia}$ (\ref{eq:eddr_Ia}).  Red lines show the accretion
  rate obtained if Compton heating acts alone, $\dot{M}_{\rm C}$
  (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion
  rate for a thermally stable flow near the stagnation radius,
  $\dot{M}_{\rm TI}$ (eq.~[\ref{eq:Mdotmax}]).  Also shown are the
  inferred accretion rates of SgrA* from \citet{Quataert:2004a} (gray
  circles), for NGC3115 from \citet{ShcherbakovWong+:2014a} (gray
  diamonds), and for Swift J1644+57 from \citet{BergerZauderer+:2012a}
  (gray triangles).  {\it Bottom panel:} Growth times $t_{\rm grow}
  \equiv \Mbh/\dot{M}_{\bullet}$ in units of the Hubble time $\th$ for
  each of the accretion rates shown in the top panel, where
  $\dot{M}_{\bullet} = \alpha\dot{M}$, where $\alpha = 0.1$, to
  account for the fraction of inflowing mass lost to disk outflows on
  small scales.}
\end{figure}

@@

Figure \ref{fig:bh_growth} (top panel) shows with solid lines the
accretion rate as a function of black hole mass for the average star
formation heating, calculated from equation (\ref{eq:eddr_analytic})
using our results for the total wind heating
(Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases
from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass
black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim
10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{8}M_{\sun}$.
These fall below the maximum thermally stable accretion rate,
$\dot{M}_{\rm TI}$ (yellow lines), although in practice high mass core
galaxies may be thermally unstable due to their deep potential wells
(we do not include the $\zeta<\zeta_c$ criterion in
Fig.~\ref{fig:mdot_mass}--see equation~\eqref{eq:cooling4} and
surrounding discussion).

For low mass black holes, blow out from SN Ia radius caps the SMBH
accretion rate at a value $\dot{M}_{\rm Ia} \sim
10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ (green lines;
eq.~[\ref{eq:eddr_Ia}]), which is however not low enough to prevent
otherwise thermally-unstable flow at smaller radii.  For higher
$M_{\bullet}$ the stagnation resides close to the Ia radius so Ia
heating contributes to the steady gas heating rate, even if the energy
released by a single Ia is insufficient to unbind gas from the stellar
bulge (eq.~[\ref{eq:blowout}]).  This explains why the black and teal lines mean at high $M_{\bullet}$.

@@

The unresolved core X-ray luminosities of nearby galactic nuclei
provide a powerful diagnostic of the SMBH accretion rates and how they
vary with SMBH mass and other galaxy properties (e.g., \citealt{Ho08}
and references therein).  Figure~\ref{fig:miller} shows our
predictions for $\langle L_{X} \rangle =\epsilon_X \dot{M} c^2$ as a
function of black hole mass, where $\epsilon_{X} = \alpha\epsilon_{\rm
  rad}\epsilon_{\rm bol}$, $\alpha = 0.1$ accounts for the fraction of
the inflowing matter loss to outflows from the accretion disk,
$\epsilon_{\rm rad}$ is the radiative efficiency of the accreted
matter, and $\epsilon_{\rm bol} = 0.1$ is the assumed bolometric
correction into the measured X-ray band for low luminosity AGN
(\citealt{Ho08}).  In all cases the value of $\langle L_X \rangle$ is
calculated using the accretion rate from the top line of
equation~\eqref{eq:mdot_analytic} with $\Gamma = 0.3
\Mbheight^{-0.24}$, based on fitting the \citet{LauerFaber+:2007a}
galaxy sample.

@@

We have calculated steady-state models for the hot gaseous
circumnuclear media of quiescent galaxies, under the assumption that
gas is supplied exclusively by stellar wind mass loss and heated by
shocked stellar winds, supernovae and black hole feedback.  We
numerically compute solutions for a range of different black hole
masses, heating rates, and observationally-motivated stellar density
profiles.  Then we use our numerical results (Table
\ref{table:models}) are used to verify and calibrate analytic
relationships (Appendix \ref{app:rs}, \ref{app:be}).  We use the
latter to explore systematically how the SMBH accretion rate varies
with black hole mass and the galaxy's SFH.  Our results for
$\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray
luminosities of quiescent SMBHs and low luminosity AGN.  Our
conclusions are summarized as follows.

@@

  \item Including the effects of heat transport by electron conduction
    results in at most order unity changes to the key properties of
    the flow (e.g. stagnation radius, mass accretion rate, and thermal
    stability) for causal values of the conduction saturation
    parameter $\phi < 0.1$ (eq.~[\ref{eq:conduction}]).  Angular
    momentum is also unlikely to invalidate our spherically symmetric
    model on large scales, given observationally inferred rotation
    rates of galactic nuclei near the stagnation radius
    ($\S\ref{sec:rotation}$).

  \item Radiative cooling has a more pronounced influence on the flow
    structure when the radiative cooling rate exceeds the gas heating
    rate near the stagnation radius, where the gas is in nearly
    hydrostatic equilibrium (Fig.~\ref{fig:TI}).  This condition is
    approximately equivalent to the $t_{\rm cool} \gg t_{\rm ff}$
    criterion for thermal instability advocated by \citet{McCourt+12}
    and \citet{Li&Bryan14a}.  The transition in the flow properties
    that occurs as heating is reduced may represent a true ``thermal
    instability" (hot ISM condensing into a cooler clouds), or it may
    simply represent an abrupt transition from a steady inflow-outflow
    solution to a global cooling flow.  We leave distinguishing
    between these possibilities to future work.

  \item The location of the stagnation radius, and hence the SMBH
    accretion rate, is a sensitive function of the gas heating rate
    $\propto v_w^{2}$.  Quantitatively, $\rs\propto v_w^{-2}$,
    implying that $\Mdot\propto v_w^{-3.8 (-2.4)}$ for fiducial core
    (cusp) galaxies.  However, $\Mdot$ can increase even more rapidly
    with decreasing $v_w$ for two reasons: (1) when $v_w$ becomes
    comparable to the stellar velocity dispersion ($\zeta < \zeta_c$;
    eq.~$[\ref{eq:zetacrit}]$), then gas remains bound to the stellar
    bulge and cannot produce a flow with a positive kinetic energy
    interior to the stellar break radius, as we show in Appendix
    \ref{app:be}; (2) For low $v_w$, gas near the stagnation radius
    becomes thermally unstable, which based on the results of previous
    numerical studies (e.g.,\citealt{Ciotti+10}) is instead likely to
    result in a burst of high accretion ($\S\ref{sec:cycle}$).
